data wrangling and plots

### 2021-02-28 shared analysis files /data_wrangling_plot22feb.Rmd
revamping and reinventing initial figures

## loading libraries 
pacman::p_load(metafor, tidyverse)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r, echo= FALSE}
#SMD across all studies
ggplot(normalized, aes(x=study_id, y=yi))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 10, angle = 45))+
  ggtitle("SMD across all studies")
```

```{r, echo= FALSE}
# scatterplot of standardized mean response faceted by exp age
ggplot(dat_MA_ES, aes(x=log(vi), y=log(yi), color = study_id))+
  geom_point()+
  theme_bw()+
  facet_wrap(~exp_age)+
  ggtitle("Log transformed SMD across log transformed variance 
          colored by study and faceted by experimental age")
```

>>>>

## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, ggsci, wesanderson)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE,build_vignettes = TRUE)
#library(orchaRd)

@@

```{r, echo= FALSE}
#SMD across all studies
glimpse(normalized)
ggplot(normalized, aes(x=reorder(study_id, -yi), y=yi, color = as.factor(experiment_id)))+
  geom_boxplot()+
  scale_color_tron()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 10, angle = 45,hjust = 1), 
        legend.position = "bottom")+
  ggtitle("SMD across all studies")

#corresponding model
fig1 <- rma.mv(yi, vi, data=dat_MA_ES, 
               random = ~1 | response_id/ experiment_id/ study_id,
                 method="REML")

fig1
```

```{r, echo= FALSE}
# scatterplot of standardized mean response faceted by exp age
ggplot(dat_MA_ES, aes(x=vi, y=yi, color = study_id))+
  geom_point()+
  theme_bw()+
  ggtitle("=SMD across variance 
          colored by study")
```

```{r}
ggplot(normalized, aes(x=exp_age, y=yi, color = as.factor(exp_age)))+
  geom_boxplot()+
  theme_bw()+
  ggtitle("SMD across different experimental ages")
```
